% Make sure to keep the text within the brackets and the output should turn out correct
\acknowledge{%
An acknowledgement of the people I would like to thank is necessarily incomplete, but starts with family.  My parents have always supported me throughout my life's adventures, fortunes and misfortunes.  My brother Ferdinand has been my best friend and biggest fan since his birth.

I chose to University of Florida to work with Simon Phillpot as my advisor, and I could not have asked for a better experience.  Susan Sinnott was influential early during this process, while Richard Hennig has been an invaluable resource.  I would also like the rest of the members of my committee.

I have worked with people that provided key insight into this project.  Jeffrey Larson and Stefan Wild at Argonne National Laboratory provided expertise with the scalability and architecture during early development phases of the optimization software.  Oliver Ruebel and Dmitriy Morozov at Lawrence Berkeley Labs introduced me to visualization and dimensionality-reduction techniques.  Stephen Foiles and Chris O'Brien at Sandia National Laboratories provided expertise and support throughout this process, while John Adam Stephens amd Michael Eldred provided insights into statistical and minimization concepts.  Finally, I would like to thank David Bai, who supervised me during an internship at Idaho National Labs.

The support of members of the Dr. Phillpot's, Dr. Hennig's, and Dr. Sinnotts research groups have provided friendship and support throughout the years.}
